Data Preparation

### 2021-07-13 x0_data-preparation.Rmd
got weird push error - inserted a line to force another commit/push

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("ggnewscale")
library(tidyverse)
library(lubridate)
library(zoo)
library(patchwork)
library(ggnewscale)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("ggnewscale")

library(tidyverse)
library(lubridate)
library(zoo)
library(patchwork)
library(ggnewscale)
